\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% personal data
\name{Francesco}{Dal Canton}
\phone[mobile]{+31~65~040~7596}
\email{fr.dalcanton@gmail.com}
\homepage{github.com/frank}

\newcommand\vspacing{0.4}

\begin{document}
\makecvtitle

I am an artificial Intelligence MSc graduate with experience in working with Deep Learning, Computer Vision, and Time Series Analysis in the medical domain.

\vskip \vspacing in

\section{Experience}

\cventry{11.2021\,--\,Present}{Deep Learning Researcher}{Medis Medical Imaging}{}{}{My role focused on researching and developing production-ready computer vision algorithms (Deep Learning-based and otherwise) for echocardiography workflow automation, along with infrastructure development and maintenance.}

\cventry{05.2021\,--\,07.2021}{Artificial Intelligence Analyst}{The Netherlands Cancer Institute}{}{}{Research role aimed at continuing and improving the work of my Master's thesis.}

\cventry{11.2019\,--\,04.2021}{Research Intern}{The Netherlands Cancer Institute}{}{}{Research role aimed at analysing data for my Master's thesis.}

\cventry{06.2019}{Research Intern}{KPN}{}{}{Research role involving Natural Language Processing and Data Mining, aimed at investigating new product directions at KPN in collaboration with the University of Amsterdam.}

\cventry{03.2018\,--\,06.2018}{Teaching Assistant}{University of Groningen}{}{}{Held tutorials and designed and graded assignment for the BSc Neural Networks course at the University of Groningen.}

\cventry{03.2018\,--\,08.2018}{Research Intern}{Universitair Medisch Centrum Groningen}{}{}{Research role aimed at analysing data for my Bachelor's thesis}

\vskip \vspacing in

\section{Education}
\cventry{2018\,--\,2021}{MSc in Artificial Intelligence (Cum Laude)}{University of Amsterdam}{Amsterdam (NL)}{Grade average: 8.2/10}
{An abstract of my thesis on \emph{Multiple-Instance Learning for Assessing Prognosis of Ductal Carcinoma In Situ} was accepted for an oral presentation at the European Congress of Pathology of 2021, and follow-up research based on my work was published at SPIE (\url{https://doi.org/10.1117/12.2612838}).}
\vskip 0.1in
\cventry{2015\,--\,2018}{BSc in Artificial Intelligence (Honours in Philosophy)}{University of Groningen}{Groningen (NL)}{Grade average: 8/10}
{A paper resulting from my thesis on \emph{Early Detection of Sepsis Induced Deterioration Using Machine Learning} was published in the proceedings of the BENELEARN2018 conference (\url{https://doi.org/10.1007/978-3-030-31978-6_1}).}
\vskip 0.1in
\cventry{2010\,--\,2015}{Diploma di Maturità Classica}{Liceo Classico "G. Marconi"}{Conegliano (IT)}{Grade: 83/100}

\vskip \vspacing in

\section{Skills}
\cvitem{Operating Systems}{Experienced user of both Windows and Linux-based operating systems and standard software}{}
\cvitem{Programming Languages}{Proficient with Python. Basic knowledge of Java, C, Matlab, R, SQL, Prolog}
\cvitem{Notable Python APIs}{Proficient with PyTorch, PyTorch Lightning, Scikit-learn, Pandas, Tensorboard, OpenSlide, gRPC, H5PY}
\cvitem{Miscellanea}{Proficient with Git, Linux shell, Latex. Familiar with Docker, Singularity.}

\vskip \vspacing in

\section{Languages}
\cvitemwithcomment{Italian}{C2}{Mothertongue}
\cvitemwithcomment{English}{C2}{IELTS 8.5 (in 2014)}

\vskip \vspacing in

\section{Personal skills}
\cvitem{Individual}{Organised, detail oriented, proficient at analytical thinking and problem solving}
\cvitem{Team Skills}{Diplomatic, strong at team building, communication, and at forming rapport}
\cvitem{Public Speaking}{Strong presentation skills}

\vskip \vspacing in

\section{Extras}
\cvitem{Driving License}{Italian A1 and B}


\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}

\end{document}
